State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed non-reduced model to full neural field model in the paper

\section{Results}\label{ResultsSection} The non-reduced neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.

@@

   	\caption{\textbf{a.} Example of data generated by the non-reduced model. \textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.} 

@@

The accuracy for state estimates were evaluated by comparing the field reconstruction (see equation~\ref{DefFieldDecomp}) to the true field using the mean (over time) of the root mean square error (MRMSE) (over space) and standard deviation of the RMSE. The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}. A snapshot of the true field, the estimated field and their corresponding error is illustrated in Figure~\ref{fig:FieldEstimate}. This figure highlights the loss of the high spatial frequency information in the basis function decomposition.
  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). The error remains consistent over time.} 
\label{fig:RMSE}
   \end{figure}
\begin{figure*}[!th]
\centering 
\subfigure[][]{\label{fig:TrueField}\includegraphics[scale=1]{./Graph/TrueField90.pdf}}
\subfigure[][]{\includegraphics[scale=1]{./Graph/EstimatedField90.pdf}}
\subfigure[][]{\includegraphics[scale=1]{./Graph/EstimationError90.pdf}}\\
\caption{Examples of the neural fields. \textbf{a.} The true field from the non-reduced model which was used to generate data. \textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. \textbf{c.} The absolute error between the true and reconstructed fields, the error shows high frequency behaviour.}
\label{fig:FieldEstimate}
\end{figure*}

>>>>

\section{Results}\label{ResultsSection} The full neural field model derived in Section~\ref{NeuralModelSection} was used to generate the data for state and parameter estimation. All parameters for the model are given in Table~\ref{tab:Model Parameters}. Figure~\ref{fig:experimental design}(a) shows example data from the sensors of the model, and Figure~\ref{fig:experimental design}(b) shows the power spectral density (PSD) of the simulated time-series. The PSD shows the typical $1/f^2$ characteristics of intracranial EEG.

@@

   	\caption{\textbf{a.} Example of data generated by the full neural field model. \textbf{b.} Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of iEEG.} 

@@

The accuracy for state estimates were evaluated by comparing the field reconstruction (see equation~\ref{DefFieldDecomp}) to the true field using the mean (over time) of the root mean square error (MRMSE) (over space) and standard deviation of the RMSE. The RMSE of the field estimates over time for 100 realisations is shown in Figure~\ref{fig:RMSE}. A snapshot of the true field, the estimated field and their corresponding error is illustrated in Figure~\ref{fig:FieldEstimate}. This figure highlights the loss of the high spatial frequency information in the basis function decomposition.
  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The mean of average RMSE of the estimated field over 100 realisations (solid line) and the 95~\% confidence interval (grey region). The error remains consistent over time.} 
\label{fig:RMSE}
   \end{figure}
\begin{figure*}[!th]
\centering 
\subfigure[][]{\label{fig:TrueField}\includegraphics[scale=1]{./Graph/TrueField90.pdf}}
\subfigure[][]{\includegraphics[scale=1]{./Graph/EstimatedField90.pdf}}
\subfigure[][]{\includegraphics[scale=1]{./Graph/EstimationError90.pdf}}\\
\caption{Examples of the neural fields. \textbf{a.} The true field from the full neural field model which was used to generate data. \textbf{b.} The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. \textbf{c.} The absolute error between the true and reconstructed fields, the error shows high frequency behaviour.}
\label{fig:FieldEstimate}
\end{figure*}
